Hazelnut: A Bidirectionally Typed \\ Structure Editor Calculus

### 2016-06-22 hazelnut-popl17.tex
added .bib

\section{Hazelnut, Formally}
\label{sec:hazel}
\todo{revise text}\todo{add let and ifz}Hazelnut is based on the simply-typed lambda calculus extended with a single base type, $\tnum$. Its major constituents, introduced by example in the previous section, are:
\begin{itemize}
\item \textbf{H-types} and \textbf{H-expressions} (Sec. \ref{sec:holes}), which are terms with \emph{holes}. Holes mark subterms that are ``under construction.'' H-types classify H-expressions according to a {bidirectionally typed} static semantics.
\item \textbf{Z-types} and \textbf{Z-expressions} (Sec. \ref{sec:cursors}), which superimpose a single \emph{focus} onto H-types and H-expressions (using Huet's \emph{zipper pattern} \cite{JFP::Huet1997}.)
\item \textbf{Actions} (Sec. \ref{sec:actions}), which move the focus or modify the subterm in focus.

@@

The syntax of \emph{actions}, $\alpha$, some of which involve \emph{directions}, $\delta$, or \emph{shapes}, $\varphi$, is given in Figure \ref{fig:action-syntax}. Actions are performed on Z-types and Z-expressions according to the \emph{action semantics} of Hazelnut, which is organized around three judgements:
\[\arraycolsep=10pt\begin{array}{ll}
%\textbf{Judgement Form} & \textbf{Description}\\
\performTyp{\ztau}{\alpha}{\ztau'} & \text{Performing $\alpha$ on $\ztau$ produces $\ztau'$}\\
\performSyn{\hGamma}{\zexp}{\htau}{\alpha}{\zexp'}{\htau'} & \text{Performing $\alpha$ on $\zexp$ when $\removeSel{\zexp}$ synthesizes type $\htau$}\\
& \text{produces $\zexp'$ such that $\removeSel{\zexp'}$ synthesizes type $\htau'$}\\
\performAna{\hGamma}{\zexp}{\htau}{\alpha}{\zexp'} & \text{Performing $\alpha$ on $\zexp$ when analyzing $\removeSel{\zexp}$ against $\htau$}\\
& \text{produces $\zexp'$, such that $\removeSel{\zexp'}$ can also be analyzed}\\
& \text{against $\htau$}
\end{array}\]

@@

\bibliography{../research}}
%\softraggedright
%P. Q. Smith, and X. Y. Jones. ...reference text...

>>>>

\section{Hazelnut, Formally}
\label{sec:hazel}
\todo{revise text}\todo{add let and ifz}\todo{make eqn numbering work better}Hazelnut is based on the simply-typed lambda calculus extended with a single base type, $\tnum$. Its major constituents, introduced by example in the previous section, are:
\begin{itemize}
\item \textbf{H-types} and \textbf{H-expressions} (Sec. \ref{sec:holes}), which are terms with \emph{holes}. Holes mark subterms that are ``under construction.'' H-types classify H-expressions according to a {bidirectionally typed} static semantics.
\item \textbf{Z-types} and \textbf{Z-expressions} (Sec. \ref{sec:cursors}), which superimpose a single \emph{focus} onto H-types and H-expressions (using Huet's \emph{zipper pattern} \cite{JFP::Huet1997}.)
\item \textbf{Actions} (Sec. \ref{sec:actions}), which move the focus or modify the subterm in focus.

@@

The syntax of \emph{actions}, $\alpha$, some of which involve \emph{directions}, $\delta$, or \emph{shapes}, $\varphi$, is given in Figure \ref{fig:action-syntax}. Actions are performed on Z-types and Z-expressions according to the \emph{action semantics} of Hazelnut, which is organized around three judgements:\todo{fix spacing}
\[\arraycolsep=10pt\begin{array}{ll}
%\textbf{Judgement Form} & \textbf{Description}\\
\performTyp{\ztau}{\alpha}{\ztau'} & \text{Performing $\alpha$ on $\ztau$ produces $\ztau'$}\\
\performSyn{\hGamma}{\zexp}{\htau}{\alpha}{\zexp'}{\htau'} & \text{Performing $\alpha$ on $\zexp$ when $\removeSel{\zexp}$ synthesizes type $\htau$}\\
& \text{produces $\zexp'$ such that $\removeSel{\zexp'}$ synthesizes type $\htau'$}\\
\performAna{\hGamma}{\zexp}{\htau}{\alpha}{\zexp'} & \text{Performing $\alpha$ on $\zexp$ when analyzing $\removeSel{\zexp}$ against $\htau$}\\
& \text{produces $\zexp'$, such that $\removeSel{\zexp'}$ can also be analyzed}\\
& \text{against $\htau$}
\end{array}\]

@@

\bibliography{bibliography}
%\softraggedright
%P. Q. Smith, and X. Y. Jones. ...reference text...
